Large Language Models in Reinforcement Learning - A Comparison of Methods

### 2023-10-03 doc/paper.tex
add paragraph on reward function method

LLM integration into the reward function, where actions similar to those suggested by the LLM grant a small auxilliary reward. The agent is trained as in the baseline.

>>>>

The agent is trained as in the baseline. The agent's state observation is encoded to natural text, and sent as part of a prompt to the LLM. This may be done at every timestep, or after some interval of timesteps. In addition to the state observation, the LLM is also asked to respond with a list of recommendations. These recommendations can be proposed actions for the agent to perform, or goal states that the agent should reach. The agent then acts independently of the LLM for one or more timesteps, as dictated by the baseline RL algorithm it is trained with. As it does so, its actions are tracked and encoded to natural text. Alternatively, a new state observation is generated after the timesteps, and also encoded as natural text. Then, the LLM is used as a tool for semantic similarity comparison, comparing either its own formerly proposed actions to the actions performed by the agent, or comparing its proposed goal state to the new state reached by the agent. Finally, high semantic similarity gives an additional reward which is implemented in the reward function of the agent.
